An Improved Metric for the Analysis of Swarms

### 2018-04-19 paper.tex

\begin{abstract}
An important criterion in the assessment of swarm coordination algorithms is
the extent to which they cause unnecessary movement, i.e. movement which
occurs as a side affect of the algorithm rather than the the intended
function. This paper examines the widely used distance metric as a mechanism
to measure the internal movement of agents and introduces a new
\emph{cohesion/repulsion metric}.  Both metrics are based upon the resultant
internal movement of a swarm identified by analysing the changes in the
inter-agent interactions. The two metrics differ in their approach to
identifying the changes. The distance metric uses variations in the
inter-agent distances and the new metric uses the resultant magnitudes from
the agents' \emph{inter-agent vector magnitudes}  which we claim offers a
number of advantages over the distance metric.  Both metrics allow a
comparison of the effects of different swarming algorithms on a swarm's
structure to identify the `level' of change in a swarm's internal structure
which is an indication of the amount of unnecessary movement an algorithm
creates.  In addition the \emph{cohesion/repulsion} metric also identifies a
swarm as expanding or cohesive which can be used in the analysis of a swarm 
filling a space to identify an exit condition.
\end{abstract}

@@

\newpage

>>>>

\begin{abstract}
  An important criterion in the assessment of swarm coordination algorithms is
  the extent to which they cause unnecessary movement, i.e. movement which
  occurs as a side effect of the algorithm rather than from the fulfilment of
  the intended function of the swarm. This paper examines the widely used
  distance metric as a mechanism to measure the internal movement of agents,
  introduces an entirely new \emph{cohesion/repulsion metric}, and compares and
  contrasts the two.  Both metrics are based upon the resultant internal
  movement of a swarm, identified by analysing changes in inter-agent
  interactions. The metrics differ in their approach to identifying the
  changes. The distance metric uses variations in inter-agent distances,
  whereas the new metric is based on the magnitudes of \emph{inter-agent
  cohesion and repulsion vectors}. The cohesion/repulsion metric offers a
  number of advantages over the distance metric.  Both metrics allow a
  comparison of the effects of different swarming algorithms on the `amount of
  change' in a swarm's internal structure, giving an indication of the amount
  of unnecessary movement that an algorithm generates. In addition, the
  \emph{cohesion/repulsion} metric also allows the identification of the
  essential characteristic of a swarm as `expanding', `stable', or
  `contracting'. This opens up the possibility of using the cohesion/repulsion
  metric in ways that are not possible with the distance metric in practical
  swarming applications, such as area filling and reconnaissance.
\end{abstract}

@@

\clearpage
